\newpage

\begin{center}
	\textcolor{white}{kjbkjjkbjjhjh}\\
	\vspace{2cm}
	\textbf{\textit{\Huge{\textcolor{myblue}{Abstract}}}}
	\vspace{2cm}
	
	\begin{minipage}{0.75\textwidth}
		\addcontentsline{toc}{chapter}{Abstract}
		
		\paragraph{}This document presents the project aimed at distributing a stock of illustrations produced by URG\'eo to contribute to education on risk factors in Haiti. The project, named \texttt{\projectName}, involves designing an IT solution that will allow these illustrations to be distributed first in Haiti and then globally. \vspace{0.5cm}
		 
		\paragraph{} The first step in carrying out our project is to assess the client's needs, and to take stock of the concepts that concern the project. Once this work completed, the development team proposed building an e-library to address the problem.\par
		\paragraph{}Next come the necessary analyses to ensure the smooth progress of the website construction. On the one hand, we explore project methodologies and frameworks, review existing methodologies and frameworks for website creation, and choose the methodology and framework to use for the remainder of the project. On the other hand, we analyze the risks that could affect the project's progress and plan the actions to be taken to mitigate these risks as well as the responses to have if any of the anticipated risks occur, in order to minimize their impact on the project.\par
		\paragraph{}The next phase is design. In this part, we model the project to identify the functionalities to be implemented, choose the architecture to adopt for the site, select the tools and technologies to use, and create the data model for building the database.\par
		\paragraph{}Finally, we present the project after its construction by detailing the implemented functionalities and the steps to follow for its use, both for regular site users and for administrators.\vspace{0.5cm}
		
		\paragraph{} \noindent This work, funded by the UNDP, is carried out as part of our final project in electronic engineering and, we hope, will help better educate the Haitian population on the concepts covered by the various illustrations that will be distributed.
	\end{minipage}
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
\end{center}